---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wqplot

<!-- badges: start -->
<!-- badges: end -->

The goal of wqplot is to allow you to visualize wq data with different kinds of plots.

## Installation

You can install the development version of testfunctions from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("catarfish/testfunctions")
```

## Example

To start using the package:
```{r example}
library(testfunctions)
```

Look at data
```{r}
summary(YBFMP_WQ)
```

Functions

* `Yearbox` plots a wq variable boxplot by station (StationCode) and water year (WY)
* `Monthbox` plots a wq variable boxplot by station and month
* `VisPoint` plots a wq variable point plot by Datetime and Station
* `Vishist` plots a wq variable histogram by Station and your bin of interest
* `PlotVars` plots two variables against each other and colors by station
* `c2f` converts celsius to fahrenheit

