---
title: "package_code"
author: "Catarina Pien"
date: "3/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(devtools)
library(usethis)
library(available)
```

Figure out where you want your package to be saved on your local computer
```{r}
setwd('..')
getwd()
create_package("testfunctions")
```

Connect go git
```{r}
usethis::use_git()
```

Connect to github
```{r}
usethis::use_github()
```

Add license
```{r}
usethis::use_apache_license()
```

Need to build readme when you update readme. 
```{r}
usethis::use_readme_rmd()
devtools::build_readme()
```

* Run this, which will create a script and a folder. 
* Add your raw data to folder
* Run any code you want to convert your raw data to clean data. 

```{r}
use_data_raw()
```

* Run use_data() from your cleaning data R script to write your clean data file to the data folder. 
```{r}
usethis::use_data()
```

# Name your functions here. Will create an R script. 
```{r}
usethis::use_r("wqplots.r")
usethis::use_r("celstofahr.r")
usethis::use_r("makeplot.r")
```



```{r}
use_package("dplyr")
use_package("ggplot2")
```

```{r}
use_package_doc()
```

What packages are needed?
```{r}
use_import_from("ggplot2", "ggplot")
use_import_from("magrittr", "%>%") # will be in namespace and document for pipe

# Put in import of DESCRIPTION file
# package documentation usethis::use_package_doc() 
# use_import_from(package, function) 
# devtools::document() to put it in NAMESPACE
```

# Add roxygen2 documentation to your script, then run this function below to create files for your documentation. Will add to DESCRIPTION file, NAMESPACE file, functions. 
```{r}
devtools::document()
```

Test functions
```{r}
use_test("testfunctions.R")
```

```{r}
devtools::check()
```

